

1) Get the the ship running with multiple waypoints - including going back on the x-axis. 
2) Port that to the drone - try fly the way points on the drone
3) Potentially need to adjust the PID for XY-pos 
4) Find a way to insert a marker into the simulation - not that important
5) Vision - regonise the marker, add the new waypoint to the list - focus more
6) Genereal tuning of everything. 



list of goals: 
1) Achieve the drone can follow a track of markers - uses the orientation of the marker/or use information encoded into the marker to know its new orientation.  
2) Achieve encoding information in visual markers/visual communication with  the drone.
3) E-book reader for wasy way to change the markers 
4) Test the general robustness of the system by testing inside and outside. 
5) General understanding of GNC 


More time: 
Marker - height information - either on this marker or from this to the new marker.
marker that encodes the landing point - or maybe the end point (then it has to return and backtrack its route)  

keep it simple, stupid
test each part individually on the drone


VIsion: 
1) reading and type of markers (qr code) done
 - implement a reader.
2) convert into something useable (splitting str and converting it to x,y,z)
3) feed the new reference to the controller 
4) fix the bias 

our idea: 
so potentially issues: 
constant video feed. 


string includes the follwing: 
the current markers position in absolute coordinates (x,y)
the next waypoint position (x,y,z) 
perhaps a flag (starter marker, landing marker, passby marker, stop for 20 sec and fly again marker)

next steps: 
find out how bad the cam feed is on the drone (can it read the qr crode - one to two meters away from it) / check on the erader /or same size as ebookreader  
implement the qr scanner 
two parts - 1) detect the new qr code and hover over it 2)scan it 
feed the new ref to the controller
test and fix th bias function



backup: 
lookup table and 5/6 homemade markers we can compare the vision data with. 




